### 2024-03-01 ms.qmd
Updates

```{r}
#| label: setup
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot)
```

@@

@@

pmcmc <- format_p(sapply(estimates, pmcmc), 4)

@@

  pmcmc = rep(pmcmc, each = 1)

@@

  rename('pmcmc' = 'pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table

@@

knitr::knit_print(real_table)

@@

Both species learnt across all treatments  (?@tbl-data), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-deli). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-guich).

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for L. delicata. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_deliA <- df_fig(as.data.frame(deli), "L. delicata") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
deliB_list <- list(
  'CORT-Cold' = deli_CORTCold,
  'Control-Cold' = deli_ControlCold,
  'CORT-Hot' = deli_CORTHot,
  'Control-Hot' = deli_ControlHot)
df_deliB1 <- data.frame(
  Value = unlist(deliB_list),
  Treatment = factor(rep(names(deliB_list), each = length(deli_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_deliB2 <- df_deliB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_deli <- plotting(df_prob = df_deliA, df_violin = df_deliB1, df_points = df_deliB2)
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_deli.png")
```

```{r, fig-guich}
#| label: fig-guich
#| fig.cap: "Results for L. guichenoti. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_guichA <- df_fig(as.data.frame(guich), "L. guichenoti") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
guichB_list <- list(
  'CORT-Cold' = guich_CORTCold,
  'Control-Cold' = guich_ControlCold,
  'CORT-Hot' = guich_CORTHot,
  'Control-Hot' = guich_ControlHot)
df_guichB1 <- data.frame(
  Value = unlist(guichB_list),
  Treatment = factor(rep(names(guichB_list), each = length(guich_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_guichB2 <- df_guichB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_guich <- plotting(df_prob = df_guichA, df_violin = df_guichB1, df_points = df_guichB2)
ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_guich.png")
```

#### Results employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task

@@

pmcmc_2 <- format_p(sapply(estimates_2, pmcmc), 4)

@@

  pmcmc = rep(pmcmc_2, each = 1)

>>>>

```{r}
#| label: setup
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
```

@@

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

```{r, fig-results}
#| label: fig-results
#| fig.cap: "Results for L. delicata (A,B) and L. guichenoti (C, D). A, C) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B, D) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A and C) (df_prob)
# L. delicata
df_deliprob <- df_plotAC("deli")
# L. guichenoti
df_guichprob <- df_plotAC("guich")
#
# Create the df for the violin plots in plot B) (df_violin)
# L. delicata
df_deliV <- df_plotBD1("deli")
# L. guichenoti
df_guichV <- df_plotBD1("guich")
#
# Create the df for the points and bars in plot B) (df_points)
# L. delicata
df_deliP <- df_plotBD2("deli")
# L. guichenoti
df_guichP <- df_plotBD2("guich")
#
#
# Make plots deli and guich
source(here("R", "func.R"))
fig_deli <- plotting(sp = "deli", df_prob = df_deliprob, df_violin = df_deliV, df_points = df_deliP)
fig_guich <- plotting(sp = "guich", df_prob = df_guichprob, df_violin = df_guichV, df_points = df_guichP)
# Combine plots of both species into the final figure
fig_results <- plot_grid(fig_deli, fig_guich, ncol = 1)
ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_deli.png")
```

#### Slopes estimates per treatment and species for the original database

@@

Pmcmc <- format_p(sapply(estimates, pmcmc), 4)

@@

  Pmcmc = rep(Pmcmc, each = 1)

@@

  rename('pmcmc' = 'Pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table

@@

real_table

@@

#### Slopes estimates per treatment and species employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task

@@

Pmcmc_2 <- format_p(sapply(estimates_2, pmcmc), 4)

@@

  Pmcmc = rep(Pmcmc_2, each = 1)
